A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Proposal improvement

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful (AI) algorithms have previously found their
inspiration. Our focus was not on a single animal species but all of them,
using general abstraction to identify what those species have in common. In our
analysis, we consider a broad animal spectrum, from bacteria to humans and
lions, finding our inspiration on the biological Life Cycle of the animal
species.
